---
title: "Sports Gambling Equity Forecast and Analysis"
author: "Matthew M. Stone"
date: "May 2nd, 2021"
output: 
  html_document:
    theme: downcute_theme
    self_contained: true
    code_folding: hide
    thumbnails: false
    lightbox: true
  
---

```{r}
downcute(
  fig_width = 8,
  fig_height = 5,
  fig_caption = TRUE,
  lightbox = FALSE,
  thumbnails = FALSE,
  gallery = FALSE,
  toc_depth = 2,
  embed_fonts = TRUE,
  use_bookdown = FALSE,
  pandoc_args = NULL,
  md_extensions = NULL,
  mathjax = "rmdformats",
  highlight = NULL,
  default_style = c("light", "dark"),
  downcute_theme = c("default", "chaos"),
  ...
)
```

# Add to headers to have dropdowns {.tabset .tabset-fade .tabset-pills} 

```{r setup, message=FALSE, warning=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

## Global options
options(max.print="75")
opts_chunk$set(cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```
# Packages
```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)
library(fpp3)
library(wesanderson)
library(distributional)
library(rmdformats)


# Creating Color palette
cPal <- c("#009E73", "black", "red", "#0072B2", "#D55E00")
```


# Exploratory Data Analysis
* Variables to consider: 
  + date 
  + open 
  + high 
  + low
  + close
  + volume (volume of shares that are transacted) 
  + adjusted (adjusted close price of stock)
  
## DraftKings
### Ticker - DKNG
```{r, cache=TRUE}
# Pull DraftKings Data
draftK <- c("DKNG") %>% 
  tq_get(., from = "2015-01-01") %>%
  as_tsibble(., 
             index = date) 

# DraftKings Adjusted close price
draftK %>% autoplot(adjusted) + 
  labs(
    title = "DraftKings Adjusted Price", 
    y = "Adjusted Stock Price ($)", 
    x = "Year (1D)", 
    subtitle = "    ") +  theme_minimal()

# DraftKings Volume 
draftK %>% 
  autoplot(volume) + 
  labs(
    title = "DraftKings Volume", 
    y = "Trade Volume", 
    x = "Year (1D)", 
    subtitle = "   ") + theme_minimal()

# Most recent day
draftK %>% 
  tail(1)

```
* Takeaways
  + Volume spikes inbetween 07/20 - 11/20ish
    
* Other notes:
  + Volume = 10,769,200



## Flutter Entertainment (FanDuel)
### Ticker - PDYPY
```{r, cache=TRUE}
# Pull FanDuel Data
fanDuel <- c("PDYPY") %>% tq_get(., from = "2018-01-01") %>%
  as_tsibble(., index = date)

# FanDuel Adjusted close price
fanDuel %>% autoplot(adjusted, 
                     color = "#0072B2") + 
  labs(
    title = "FanDuel Adjusted Price",
    y = "Adjusted Stock Price ($)", 
    x = "Year (1D)", 
    subtitle = "    ") + theme_minimal()

# DraftKings volume
fanDuel %>% 
  autoplot(volume, 
           color = "#0072B2") + 
  labs(title = "FanDuel Volume", 
       y = "Trade Volume", 
       x = "Year (1D)", 
       subtitle = "   ") +  theme_minimal()

# Most recent day
fanDuel %>% 
  tail(1)
```

* Notes:
  + Acquired by Paddy Power Betfair in 2018 (Now known as FLutter Entertainment)
  + HUGE spikes in volume after 2020
  + Large jump after covid
  + V-Shape recovery dipped at the beginning of 2021
  + Volume = 11,900

## MGM Resorts
### Ticker - MGM
```{r cache=TRUE}
# Pull MGM Data
MGM <- c("MGM") %>% tq_get(., from = "2018-01-01") %>%
  as_tsibble(., index = date)

# MGM Adjusted close price
MGM %>% autoplot(adjusted, 
                 color = "red") + 
  labs(title = "MGM Adjusted Price", 
       y = "Adjusted Stock Price ($)", 
       x = "Year (1D)", 
       subtitle = "    ") + theme_minimal()


# MGM Volume
MGM %>% autoplot(volume, 
                 color = "red") + 
  labs(title = "MGM Volume", 
       y = "Trade Volume", 
       x = "Year (1D)", 
       subtitle = "   ") + theme_minimal()

# Looking at most recent day
MGM %>% 
  tail(1)
```
* Notes:
  + Public since the 70's
  + Large jump in volume after 2020
  + Volume = 8,184,000

## Penn National Gaming
### Ticker - PENN
```{r}
# Pull PENN Data
PENN <- c("PENN") %>% tq_get(., from = "2015-01-01") %>%
  as_tsibble(., index = date)

# PENN Adjusted close price
PENN %>% autoplot(adjusted, 
                  color = "#D55E00") + 
  labs(title = "PENN Adjusted Price", 
       y = "Adjusted Stock Price ($)", 
       x = "Year (1D)", 
       subtitle = "    ") + theme_minimal()

# PENN Volume
PENN %>% autoplot(volume, 
                  color = "#D55E00") + 
  labs(title = "PENN Volume", 
       y = "Trade Volume", 
       x = "Year (1D)", 
       subtitle = "   ") + theme_minimal()

# Most recent day
PENN %>% 
  tail(2)
```

* Notes:
  + Otherwise known as Barstool sports
  + Largest spike since covid, out of all stocks
  + Dipped in Feb 2021, but recovering
  + Volume = 3,963,700


## Caesars Entertainment
### Ticker - CZR
```{r}
# Pull CZR Data
CZR <- c("CZR") %>% tq_get(., from = "2018-01-01") %>%
  as_tsibble(., index = date)

# CZR Adjusted close price
CZR %>% autoplot(adjusted, 
                 color = "#009E73") + 
  labs(title = "CZR Adjusted Price", 
       y = "Adjusted Stock Price ($)", 
       x = "Year (1D)", 
       subtitle = "    ") + theme_minimal()

# CZR Volume
CZR %>% autoplot(volume, 
                 color = "#009E73") + 
  labs(title = "CZR Volume", 
       y = "Trade Volume", 
       x = "Year (1D)", 
       subtitle = "   ") + theme_minimal()

# Most recent day
CZR %>% 
  tail(1)
```
* Notes:
  + Odd volume spike very recently
  + V-shape recovery and then some
  + Volume = 3,601,800


# Tidy Data
* Combining DraftKings, FanDuel, MGM, PENN, CZR from January 1st, 2018
  + First pulling the data
  + Issue with trading days (all starting at different dates), so creating variable PENNdays (Longest stock to pick from)
  + Filtering all stocks for when they started sports gambling
  + Joining everything together

```{r}
# Pull Data
sportGam <- c("DKNG", 
              "PDYPY", 
              "MGM", 
              "PENN", 
              "CZR") %>% 
  tq_get(., from = "2018-01-01") %>%
  as_tsibble(., index = date, key = symbol)

# Creating Longest day for trading day
PENNdays <- sportGam %>% 
  as_tibble() %>%
  filter(symbol=="PENN" & date > as.Date("2018-05-14")) %>% 
  mutate(trading_day = row_number()) %>% 
  select(date, trading_day)

# Filtering stocks to start at different times
Use.Stocks <- sportGam %>% 
  as_tibble() %>%  
  filter(
    (symbol=="DKNG" & date > as.Date("2019-12-05") | 
       (symbol=="PDYPY" & date > as.Date("2020-12-01") |
          (symbol == "MGM" & date > as.Date("2019-09-05")) |
          (symbol == "PENN" & date > as.Date("2018-05-14")) |
          (symbol == "CZR" & date > as.Date("2018-09-06"))
       )))

# Join Use.Stocks & PENNdays
Model.Me <- Use.Stocks %>% 
  as_tibble() %>% 
  left_join(., PENNdays) %>% 
  as_tsibble(index = trading_day, 
             key = symbol, 
             regular = TRUE) 

# Plotting volumes
Model.Me %>% 
  autoplot(volume) + 
  scale_color_manual(values = cPal) + 
  labs(title = "", 
       x = "Trading Days", 
       y = "Volume") + theme_minimal()

```  



# Train & Test
* Splitting train and test data sets in order to produce forecasts 2 weeks (14 trading days) out.

```{r}
# Create Test 
test <- Model.Me %>% 
  group_by(symbol) %>%
  slice_max(trading_day, 
            n = 14) %>% 
  ungroup() %>% 
  as_tsibble(index = trading_day, 
             key = symbol)

## Checking test
test

# Anti-join test out of Model.Me 
train <- anti_join(Model.Me, 
                   test) %>% 
  as_tsibble(index = trading_day,
             key = symbol)

## Checking train
train
```


# Visualizing Adjusted Prices & Volume
## Comparing All Adjusted Stock Prices
```{r}
# Adjusted Prices
train %>% 
  ggplot(aes(trading_day, 
             adjusted, 
             color = symbol)) + 
  geom_line() + 
  scale_color_manual(values=cPal) +
  labs(title = 
         "Comparing Sports Gambling Stocks Adjusted Prices", 
       y = "Stock Price ($)", 
       x = "Trading Day") + theme_minimal()

# Logged Adjusted prices
train %>% 
  ggplot(aes(trading_day, 
             log(adjusted), 
             color = symbol)) + 
  geom_line() + 
  scale_color_manual(values=cPal) +
  labs(title = "Comparing Sports Gambling Stocks", 
       subtitle =  "Log Adjusted Prices", 
       y = "Stock Price (Log)", 
       x = "Trading Day") + theme_minimal()
```

## Comparing All Trading Volumes
```{r}
# Volume
train %>% 
  ggplot(aes(trading_day, 
             volume, 
             color = symbol)) + 
  geom_line() + 
  scale_color_manual(values=cPal) +
  labs(title = "Comparing Sports Gambling Stocks Trading Volume", 
       y = "Trade Volume", 
       x = "Trading Day") + theme_minimal()


# Comparing logged volumes
train %>% 
  ggplot(aes(trading_day, 
             log(volume), 
             color = symbol)) + 
  geom_line() + 
  scale_color_manual(values=cPal) +
  labs(title = "Comparing Sports Gambling Stocks",
       subtitle = "Logged Volume",
       y = "Trade Volume (Log)",
       x = "Trading Day") + theme_minimal()
```


### Comparing all Volumes
```{r}
# Facet volume
train %>% 
  ggplot(aes(trading_day, 
             volume, 
             color = symbol)) + 
  geom_line(show.legend = F) + 
  scale_color_manual(values=cPal) +
  labs(title = "Comparing Sports Gambling Stocks Volumes",
       y = "Trade Volume", 
       x = "Trading Day") +
  facet_wrap(.~symbol,
             scales = c("free_y")) + theme_minimal()

# Facet logged volume
train %>% 
  ggplot(aes(trading_day, 
             log(volume), 
             color = symbol)) + 
  geom_line() + 
  scale_color_manual(values=cPal) +
  labs(title = "Comparing Sports Gambling Stocks", 
       subtitle =  "Logged Volume", 
       y = "Trade Volume (Log)", 
       x = "Trading Day") + 
  facet_wrap(.~symbol, 
             scales = c("free_y")) + theme_minimal()


```




# Decomposition
+ Taking a look at the decompositions of each individual stock.

## Comparing Decompositions  
```{r}
# Second Decomposition of adjusted
dcmpVol <- train %>% 
  model(stl = STL(volume))

# Looking at Volume components
dcmpVol %>% 
  components()


# Looking at Decomposition components of Volume 
dcmpVol %>%
  components() %>% 
  autoplot() + 
  scale_color_manual(values=cPal) + 
  labs(x = "Trading Day") + theme_minimal()


# Second Decomposition of adjusted
dcmpAdj <- train %>% 
  model(stl = STL(adjusted))

# Looking at Decomposition components of Adjusted
dcmpAdj %>% 
  components()


# Visualizing all of the Decompositions
dcmpAdj %>% 
  components() %>% 
  autoplot() + 
  scale_color_manual(values=cPal) + 
  labs(x = "Trading Day") + theme_minimal()

```

## CZR Decomposition 
### CZR Volume Decomposition
```{r}
components(dcmpVol) %>% 
  filter(symbol == "CZR") %>% 
  autoplot(color = '#009E73') + 
  labs(title = "STL Decomposition of CZR Volume", 
       x = "Trading Day") + theme_minimal()
```

### CZR Adjusted Stock Price Decomposition
```{r}
components(dcmpAdj) %>% 
  filter(symbol == "CZR") %>% 
  autoplot(color = '#009E73') + 
  labs(title = "STL Decomposition of CZR Adjusted Price", 
       x = "Trading Day") + theme_minimal()

```

## PENN Decomposition
### PENN Volume Decomposition
```{r}
components(dcmpVol) %>% 
  filter(symbol == "PENN") %>% 
  autoplot(color = '#D55E00') + 
  labs(title = "STL Decomposition of PENN Volume", 
       x = "Trading Day") + theme_minimal()
```

### PENN Adjusted Stock Price Decomposition
```{r}
components(dcmpAdj) %>% 
  filter(symbol == "PENN") %>% 
  autoplot(color = '#D55E00') + 
  labs(title = "STL Decomposition of PENN Adjusted Price", 
       x = "Trading Day") + theme_minimal()

```

## MGM Decomposition
### MGM Volume Decomposition
```{r}
components(dcmpVol) %>% 
  filter(symbol == "MGM") %>%
  autoplot(color = 'red') + 
  labs(title = "STL Decomposition of MGM Volume", 
       x = "Trading Day") + theme_minimal()
```

### MGM Adjusted Stock Price Decomposition
```{r}
components(dcmpAdj) %>% 
  filter(symbol == "MGM") %>% 
  autoplot(color = 'red') + 
  labs(title = "STL Decomposition of MGM Adjusted Price", 
       x = "Trading Day") + theme_minimal()

```

## FanDuel Decomposition
### Fanduel Volume Decomposition
```{r}
components(dcmpVol) %>% 
  filter(symbol == "PDYPY") %>% 
  autoplot(color = '#0072B2') + 
  labs(title = "STL Decomposition of FanDuel Volume", 
       x = "Trading Day") + theme_minimal()
```

### Fanduel Adjusted Stock Price Decomposition
```{r}
components(dcmpAdj) %>% 
  filter(symbol == "PDYPY") %>% 
  autoplot(color = '#0072B2') + 
  labs(title = "STL Decomposition of FanDuel Adjusted Price", 
       x = "Trading Day") + theme_minimal()
```

## DraftKings Decomposition
### DraftKings Volume Decomposition
```{r}
components(dcmpVol) %>% 
  filter(symbol == "DKNG") %>% 
  autoplot() + 
  labs(title = "STL Decomposition of DraftKings Volume", 
       x = "Trading Day") + theme_minimal()
```

### DraftKings Adjusted Stock Price Decomposition
```{r}
components(dcmpAdj) %>% 
  filter(symbol == "DKNG") %>% 
  autoplot() +
  labs(title = "STL Decomposition of DraftKings Adjusted Price",
       x = "Trading Day") + theme_minimal()

```



# Modeling function
```{r}
# Function
fc.model <- function(data, Outcome) {
  
	Outcome <- ensym(Outcome)
	
fits <- data %>% model(
	ARIMA = ARIMA(log(!!Outcome + 0.1)), 
	ARIMAD1 = ARIMA(log(!!Outcome + 0.1) ~ pdq(d=1)),
	ETS = ETS(log(!!Outcome + 0.1))) %>% # one way of fixing log issue
	mutate(Combo = (ARIMA + ETS)/2)
return(fits)
}



```

## Model fit and Report
```{r}
# Fit the Models
fit <- train %>% 
  fc.model(., Outcome = volume)

# ALL ARIMA reports
fit %>% select(ARIMA) %>% report()
```

### ARIMA with 1 Differencing Report
```{r}
fit %>% select(ARIMAD1) %>% report()
```
### ETS Report
```{r}
fit %>% select(ETS) %>% report()
```
### Combo Reports
```{r}
# Looking at each Combo report
fit %>% filter(symbol == "CZR") %>% select(Combo) %>% report()
fit %>% filter(symbol == "PENN") %>% select(Combo) %>% report()
fit %>% filter(symbol == "MGM") %>% select(Combo) %>% report()
fit %>% filter(symbol == "DKNG") %>% select(Combo) %>% report()
fit %>% filter(symbol == "PDYPY") %>% select(Combo) %>% report()

```


# Model Selection
## Models for CZR
```{r}
# Choosing model for CZR
fit %>% 
  filter(symbol == "CZR") %>% 
  accuracy() %>% 
  arrange(RMSE)
```

## Comparing CZR Models
### CZR ARIMA
```{r}
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "CZR") %>% 
  forecast(h = 14) %>% 
  autoplot() +
  autolayer(Model.Me %>% 
              filter(symbol == "CZR") %>% 
              select(volume)) + 
  xlim(400,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting CZR Trading Volume", 
       subtitle = "ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "CZR") %>%
  gg_tsresiduals()
```

### CZR Combo
```{r}
fit %>% 
  select(Combo) %>% 
  filter(symbol == "CZR") %>% 
  forecast(h = 14) %>% 
  autoplot() +
  autolayer(Model.Me %>% 
              filter(symbol == "CZR") %>% 
              select(volume)) + 
  ylim(0,2.5e+07) + 
  xlim(400,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting CZR Trading Volume", 
       subtitle = "ETS + ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  filter(symbol == "CZR") %>% 
  select(Combo) %>%
  gg_tsresiduals()
```

### CZR Other Models
```{r}
# Other Models (ARIMAD1)
fit %>% 
  select(ARIMAD1) %>%
  filter(symbol == "CZR") %>% 
  gg_tsresiduals()

# Other Models (ETS)
fit %>% 
  select(ETS) %>% 
  filter(symbol == "CZR") %>% 
  gg_tsresiduals()
```

* Residuals are pretty crazy for both, comparing the two models (ARIMA and Combo (ARIMA + ETS))
  + Not normally distributed (outliers)
  + For ARIMA the acf looks more like white noise with one lag outside of the bounds
  + While Combo has multiple lags outside the bounds

## Models for MGM
```{r}
# Choosing model for MGM
fit %>% 
  filter(symbol == "MGM") %>%
  accuracy() %>% 
  arrange(RMSE)
```

## Comparing MGM Models
### MGM ARIMA Model
```{r}
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "MGM") %>% 
  forecast(h = 14) %>% 
  autoplot() +
  autolayer(Model.Me %>% 
              filter(symbol == "MGM") %>% 
              select(volume)) + 
  xlim(400,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting MGM Trading Volume", 
       subtitle = "ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "MGM") %>% 
  gg_tsresiduals() + 
  labs(title = "ARIMA Model Fit")
```

### MGM Combo Model
```{r}
fit %>% 
  select(Combo) %>% 
  filter(symbol == "MGM") %>% 
  forecast(h = 14) %>% 
  autoplot() +   
  autolayer(Model.Me %>% 
              filter(symbol == "MGM") %>% 
              select(volume)) + 
  xlim(400,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting MGM Trading Volume", 
       subtitle = "ETS + ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  filter(symbol == "MGM") %>% 
  select(Combo) %>% 
  gg_tsresiduals() + 
  labs(title = "ETS + ARIMA Model Fit")
```


### MGM Other Models
```{r}
# ARIMA-D1 Model
fit %>% 
  select(ARIMAD1) %>% 
  filter(symbol == "MGM") %>% 
  gg_tsresiduals() + 
  labs(title = "ARIMA-D1 Model Fit")

# ETS Model
fit %>% 
  select(ETS) %>% 
  filter(symbol == "MGM") %>% 
  gg_tsresiduals() + 
  labs(title = "ETS Model Fit")
```

## Models for PENN
```{r}
# Choosing model for PENN
fit %>% 
  filter(symbol == "PENN") %>% 
  accuracy() %>% 
  arrange(RMSE)
```

## Comparing PENN Models
### PENN ARIMA Model
```{r}
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "PENN") %>% 
  forecast(h = 14) %>% 
  autoplot() +   
  autolayer(Model.Me %>% 
              filter(symbol == "PENN") %>% 
              select(volume)) + 
  xlim(400,780) +
  labs(x = "Trading Days",
       y = "Trade Volume", 
       title = "Forecasting PENN Trading Volume", 
       subtitle = "ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "PENN") %>% 
  gg_tsresiduals() + 
  labs(title = "ARIMA Model Fit")
```

### PENN Combo Model
```{r}
fit %>% 
  select(Combo) %>% 
  filter(symbol == "PENN") %>% 
  forecast(h = 14) %>% 
  autoplot() +  
  autolayer(Model.Me %>% 
              filter(symbol == "PENN") %>% 
              select(volume)) + 
  xlim(400,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting PENN Trading Volume", 
       subtitle = "ETS + ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% filter(symbol == "PENN") %>% 
  select(Combo) %>% 
  gg_tsresiduals() + 
  labs(title ="ETS + ARIMA Model Fit")
```

### PENN Other Models
```{r}
fit %>% 
  select(ARIMAD1) %>% 
  filter(symbol == "PENN") %>% 
  gg_tsresiduals() + 
  labs(title="ARIMA-D1 Model Fit")

fit %>% 
  select(ETS) %>% 
  filter(symbol == "PENN") %>% 
  gg_tsresiduals() + 
  labs(title = "ETS Model Fit")

```

## Models for PDYPY
```{r}
# Choosing model for PDYPY
fit %>% 
  filter(symbol == "PDYPY") %>% 
  accuracy() %>% 
  arrange(RMSE)
```

## Comparing PDYPY Models
### PDYPY ARIMA Model
```{r}
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "PDYPY") %>% 
  forecast(h = 14) %>% 
  autoplot() +   
  autolayer(Model.Me %>% 
              filter(symbol == "PDYPY") %>% 
              select(volume)) + 
  xlim(625,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting FanDuel Trading Volume", 
       subtitle = "ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "PDYPY") %>% 
  gg_tsresiduals() + 
  labs(title = "ARIMA Model Fit")
```

### PDYPY Combo Model
```{r}
fit %>% 
  select(Combo) %>% 
  filter(symbol == "PDYPY") %>% 
  forecast(h = 14) %>% 
  autoplot() +   
  autolayer(Model.Me %>% 
              filter(symbol == "PDYPY") %>% 
              select(volume)) + 
  xlim(625,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting FanDuel Trading Volume", 
       subtitle = "ETS + ARIMA: Forecasting 14 Days") + theme_minimal()



## Checking Residuals
fit %>% 
  filter(symbol == "PDYPY") %>% 
  select(Combo) %>% 
  gg_tsresiduals() + 
  labs(title = "ETS + ARIMA Model Fit")
```

### PDYPY Other Models
```{r}
# ARIMA-D1 Model
fit %>% 
  select(ARIMAD1) %>% 
  filter(symbol == "PDYPY") %>% 
  gg_tsresiduals() + 
  labs(title = "ARIMA-D1 Model Fit")

# ETS Model
fit %>% 
  select(ETS) %>% 
  filter(symbol == "PDYPY") %>% 
  gg_tsresiduals() +
  labs(title = "ETS Model Fit")
```


## Models for DKNG
```{r}
# Choosing model for DKNG
fit %>% 
  filter(symbol == "DKNG") %>% 
  accuracy() %>% 
  arrange(RMSE)
```

## Comparing DKNG Models
### DKNG ARIMA
```{r}
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "DKNG") %>% 
  forecast(h = 14) %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "DKNG") %>% 
              select(volume)) + 
  xlim(500,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting DraftKings Trading Volume", 
       subtitle = "ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  select(ARIMA) %>% 
  filter(symbol == "DKNG") %>% 
  gg_tsresiduals() +
  labs(title = "ARIMA Model Fit")
```

### DKNG Combo Model
```{r}
fit %>% 
  select(Combo) %>% 
  filter(symbol == "DKNG") %>% 
  forecast(h = 14) %>% 
  autoplot() +
    autolayer(Model.Me %>% 
                filter(symbol == "DKNG") %>% 
                select(volume)) + 
xlim(500,780) +
  labs(x = "Trading Days", 
       y = "Trade Volume", 
       title = "Forecasting DraftKings Trading Volume", 
       subtitle = "ETS + ARIMA: Forecasting 14 Days") + theme_minimal()

## Checking Residuals
fit %>% 
  filter(symbol == "DKNG") %>% 
  select(Combo) %>% 
  gg_tsresiduals() + 
  labs(title = "ETS + ARIMA Model Fit")
```


### DKNG Other Models
```{r}
fit %>% 
  select(ARIMAD1) %>% 
  filter(symbol == "DKNG") %>% 
  gg_tsresiduals() +
  labs(title = "ARIMA-D1 Model Fit")

fit %>% 
  select(ETS) %>% 
  filter(symbol == "DKNG") %>% 
  gg_tsresiduals() + 
  labs(title = "ETS Model Fit")

```


# Best Model Fits
```{r}
# Create fctest forecasting 14 periods out
## Looking at the accuracy in our test data arranged by RMSE
fctest <- fit %>% 
  forecast(h = 14) %>% 
  accuracy(test) %>% 
  arrange(RMSE) %>% 
  group_by(symbol) %>% 
  slice_min(RMSE, 
            n = 1, 
            with_ties = F)

# Best models for each Symbol
fctest


# Creating Model.Table  based on the fit
model.table <- 1:5 %>% 
  sapply(function(x) fit %>% 
           filter(symbol == fctest$symbol[[x]]) %>% select(fctest$.model[[x]]))


model.table
```


# Forecasting Test Data
```{r}
# Creating a forecast for each
testfit <- test %>% 
  fc.model(., Outcome = volume)

testfit
```

## CZR Forecasts and Plot
```{r}
# For CZR, ETS was best model
CZR_best <- testfit %>% 
  filter(symbol == "CZR") %>% 
  forecast(h=14)

## Plotting the best model for CZR
CZR_best %>% 
  filter(.model == "ETS") %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "CZR") %>% 
              select(volume)) +
  labs(x = "Trading Days", 
       y = "Trade Volume (Log)", 
       title = "Forecasting CZR Trading Volume", 
       subtitle = "Best Model - ETS: Forecasting 14 Days") + theme_minimal()
```

## DKNG Forecasts and Plot
```{r}
# For DKNG, ETS was best model
DKNG_best <- testfit %>% 
  filter(symbol == "DKNG") %>% 
  forecast(h=14)

# Plotting the best model for DKNG
DKNG_best %>% 
  filter(.model == "ETS") %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "DKNG") %>% 
              select(volume)) +
  labs(x = "Trading Days", 
       y = "Trade Volume (Log)", 
       title = "Forecasting DraftKings Trading Volume", 
       subtitle = "Best Model - ETS: Forecasting 14 Days") + theme_minimal()
```

## MGM Forecasts and Plot
```{r}
# For MGM, ARIMA was best model
MGM_best <- testfit %>% 
  filter(symbol == "MGM") %>% 
  forecast(h=14)

# Plotting the best model for MGM
MGM_best %>% 
  filter(.model == "ARIMA") %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "MGM") %>% 
              select(volume)) +
  labs(x = "Trading Days", 
       y = "Trade Volume (Log)", 
       title = "Forecasting MGM Trading Volume", 
       subtitle = "Best Model - ARIMA: Forecasting 14 Days") + theme_minimal()
```

## FanDuel Forecasts and Plot
```{r}
# For fanDuel, ETS was best model
fanDuel_best <- testfit %>% 
  filter(symbol == "PDYPY") %>% 
  forecast(h=14)

# Plotting the best model for PDYPY
fanDuel_best %>% 
  filter(.model == "ETS") %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "PDYPY") %>% 
              select(volume)) +
  labs(x = "Trading Days",
       y = "Trade Volume (Log)", 
       title = "Forecasting FanDuel Trading Volume", 
       subtitle = "Best Model - ETS: Forecasting 14 Days") + theme_minimal()
```


## PENN Forecasts and Plot
```{r}
# For PENN, ETS was best model
PENN_best <- testfit %>% 
  filter(symbol == "PENN") %>% 
  forecast(h=14)

# Plotting the best model for PENN
PENN_best %>% 
  filter(.model == "ETS") %>% 
  autoplot() + 
  autolayer(Model.Me %>% 
              filter(symbol == "PENN") %>% 
              select(volume)) +
  labs(x = "Trading Days", 
       y = "Trade Volume (Log)", 
       title = "Forecasting PENN Trading Volume", 
       subtitle = "Best Model - ETS: Forecasting 14 Days") + theme_minimal()

```




# Model Proofing
## Different way to look at accuracy 
```{r}
testfit <- fc.model(train, Outcome = volume) %>% forecast(h=14)

testfit  
```

### CZR Accuracy 
```{r}
accuracy(testfit,test) %>% filter(symbol == "CZR") # ETS
```

### PENN Accuracy
```{r}
accuracy(testfit,test) %>% filter(symbol == "PENN") # ETS
```

### MGM Accuracy
```{r}
accuracy(testfit,test) %>% filter(symbol == "MGM") # ARIMA
```

### PDYPY Accuracy
```{r}
accuracy(testfit,test) %>% filter(symbol == "PDYPY") # ETS
```

### DKNG Accuracy
```{r}
accuracy(testfit,test) %>% filter(symbol == "DKNG") # ETS
```


